\chapter{Results and Findings} 
% Main chapter title

\label{Chapter6} 
%Call reference to this chapter use \ref{ChapterX}

\lhead{Chapter 6. \emph{Results and Findings}} 
% Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

\doublespacing
% LINE FORMATTING

%\clearpage
%\pagebreak

% MAIN SECTION ==============================

\section{Phase 1}

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1.5ex]
	
	\item \textbf{Devil Advocation Test.}
	This activity has been successfully achieved. It has been found the method can detect unmatched numbers of commas, unsuitable data types during data importation from CSV to PostgreSQL database and identify the uniqueness of rows and columns in data. Results and detailed information is provided in Appendix B.2 to B.4.
	
	\item \textbf{Golang programming for import CSV files into PostgreSQL database.}
	This activity has been successfully achieved. The program is capable to read 100 rows of data from three datasets and import into PostgreSQL database. Results and detailed information is provided in Appendix H.
	
	\pagebreak
	
	\item \textbf{Sequential and concurrent programming with Golang on PostgreSQL database retrieval.}
	This activity has been successfully achieved. The program is capable to prove concurrent processing is faster than sequential in data retrieval with PostgreSQL database. Results and detailed information is provided in Appendix G.
	
	\item \textbf{Sequential and concurrent programming with Golang on reading CSV files.}
	This activity has been successfully achieved. The program is capable to prove concurrent processing is faster than sequential in reading CSV data. Results and detailed information is provided in Appendix F.
	
\end{enumerate}

